Evolutionary stretegies

### 2015-12-07 evolutionaryComputation/notes4.tex
notes of lesson 5
notes from lecture 7?

\end{document}

>>>>

\section{Time complexity}
Convergence speed: easy problems easier to calculate

population should be large enough, reasonably.

Gentic programming uses extreme high selection pressure
	creating lisp with GA's.

Using this allows much better scalimg of the algortihm.

\section{Population sizing}
\subsection{Random walks}
\[ P_N(x) = Probablity of reaching state N in postition x?\]
Gamblers ruin

\subsection{Exam}
How does it work. How does it scale up?

\section{Map labeling}
Has a bunch of little local optimum features.

all the little conditions were pulled from the fitness function
and put in the local optimizer. This meant they didn't have to
invent a bunch of weights.

Don't put everything in a fitness function. Especially if you have
to invent weights.

Excact is better, but GA's tend to scale better.

Try to keep the fitness function simple.
\end{document}
